%-----------TRAININGS-----------%
\section{Trainings}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Complete Android: Learn creating apps} $|$ \emph{Udemy}}    {Jan. 2024}
    \resumeItemListStart
        \resumeItem {Android, Java, Material Design.}
        \resumeItem {Certification Number: UC-845b0136-e1c0-426c-9d32-050ea34ecc4b.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Targeted Training for Middle Managers} $|$ \emph{Ciklum}}    {Sept. 2019}
    \resumeItemListStart
        \resumeItem {Equipping Team Leads and Managers with the best practices in people management and client relationship.}
    \resumeItemListEnd

        \resumeProjectHeading
    {\textbf{Aws Architect Training} $|$ \emph{Ciklum}}    {Feb. 2021}
    \resumeItemListStart
        \resumeItem {Architecting in the Cloud - Overview of Core AWS Services.}
        \resumeItem {Security and Compliance - Identity, Authentication and Authorization.}
        \resumeItem {Overview of Services for Web Application Architecture - Elasticity, Bootstrapping - Data Storage Scaling.}
        \resumeItem {Overview of AWS Services for Batch Processing Architecture - Designing for Cost - Disaster Recovery - Migrating Existing Applications}
    \resumeItemListEnd
        \resumeProjectHeading
    {\textbf{Cyber Security Testing Training} $|$ \emph{Ciklum}}    {Dec. 2020}
    \resumeItemListStart
        \resumeItem {Technical Introduction to penetration testing.}
    \resumeItemListEnd
        \resumeProjectHeading
    {\textbf{Scrum Master Accredited Certification} $|$ \emph{International Scrum Institute}}    {Sept. 2012}
    \resumeItemListStart
        \resumeItem {International scrum institute (70137149178136)}
    \resumeItemListEnd
        \resumeProjectHeading
    {\textbf{ISTQB certification training} $|$ \emph{ISTQB}}    {Sept. 2011}
    \resumeItemListStart
        \resumeItem {Training for the ISTQB Metodology certification.}
    \resumeItemListEnd
        \resumeProjectHeading
    {\textbf{Cisco Certified Network Asociate} $|$ \emph{Academia Alcantara}}    {Jun. 2007}
    \resumeItemListStart
        \resumeItem {CCNA - Curriculum 3.11}
    \resumeItemListEnd
        \resumeProjectHeading
    {\textbf{Network Management and Internet} $|$ \emph{Academia Alcantara}}    {April. 2007}
    \resumeItemListStart
        \resumeItem {Network Management training}
    \resumeItemListEnd
        \resumeProjectHeading
    {\textbf{English for Work and Travel} $|$ \emph{University of Córdoba - Fundecor}}    {Jul. 2006}
    \resumeItemListStart
        \resumeItem {Improve English language for common Work and Travel situations.}
    \resumeItemListEnd

\resumeSubHeadingListEnd